\documentclass[DM,lsstdraft,toc]{lsstdoc}

\setDocChangeRecord{%
\addtohist{1.1}{2004-06-23}{Initial version (Document-139).}{J.~Kantor}
\addtohist{1.2}{2011-07-12}{Updated for PDR.}{J.~Kantor}
\addtohist{1.3}{2014-03-07}{Updated for construction phase.}{J.~Kantor}
\addtohist{1.4}{2014-10-21}{SQuaRE section added.}{J.~Kantor}
\addtohist{1.5}{2014-10-30}{Added LDM-294 handle.}{J.~Kantor}
\addtohist{2.0}{2015-03-11}{Updated with new RFC process, realignment of TCT, SAT, DMLT.}{J.~Kantor}
\addtohist{3.0}{2017-06-30}{Complete overhaul of content, with all new authors. Rewritten in LaTeX. Approved for release by W.~O'Mullane.}{W.~O'Mullane}
\addtohist{3.1}{2017-07-04}{Minor cleanups for review. Approved in \jira{RFC-358}.}{W.~O'Mullane}
\addtohist{3.2}{2017-07-19}{Editorial fixes and refresh schedule and component  diagrams}{W.~O'Mullane}
\addtohist{3.3}{2017-08-21}{Update CCB and SE groups. Add Science Platform Scientist. Add section on design reviews. Approved in \jira{RFC-373}.}{W.~O'Mullane}
\addtohist{3.4}{2017-12-21}{Org chart refresh - rules for review of epics \jira{DM-7501}}{W.~O'Mullane}
\addtohist{3.5}{2018-06-18}{New DM product tree and revised org chart. Add deputy subsystem scientist. Approved in \jira{RFC-493}}{J.~Swinbank}
\addtohist{3.6}{2019-01-29}{Review product tree. Add release management subsection. Update DMCCB and DMSE team. Approved in \jira{RFC-561}}{G.~Comoretto}
\addtohist{3.7}{2019-02-06}{Add text for LSP and Middleware mangers. Time allocation policy for institutional scientists, add admin names to org chart. Approved in \jira{RFC-572}}{W.~O'Mullane, L.~Guy}
\addtohist{3.8}{2019-07-29}{Updates to Org charts, glossary, third party software, risk management, milestones. Approved in \jira{RFC-621}}{W.~O'Mullane, L.~Guy}
\addtohist{3.9}{2020-03-07}{Update SST org chart, add Middleware and Science Platform teams, provide more details on responsibility for debugging builds and hosting releases. \jira{RFC-666}, \jira{DM-22393}}{W.~O'Mullane}
\addtohist{4.0}{2020-08-18}{Clarify requirements traceability. Refresh org,doc  charts - general update for review. Gantt from milestones sub module\jira{RFC-708}}{J.~Swinbank, W~O'Mullane}
}

\title[DM PMP]{Data Management Organization and Management}

\author   {William O'Mullane, John Swinbank, Mario Juric, Leanne Guy and DMLT}
\setDocRef      {LDM-294} % the reference code
\setDocDate     {\today}              % the date of the issue
\setDocUpstreamLocation{\url{https://github.com/lsst/LDM-294}}

%
% a short abstract
%
\setDocAbstract {
This management plan covers the organization and management of the Data Management (DM) subsystem during the development, construction, and commissioning of LSST.
It sets out DM goals and lays out the management organization roles and responsibilities to achieve them.
It provides a high level overview of DM architecture, products and processes.
It provides a structured starting point for understanding DM and pointers to further documentation.}

\input{aglossary.tex}
\makeglossaries

\begin{document}
%
% the title page
%
\maketitle

%\printnoidxglossaries
%
% It's all yours from here on
%
\input{intro}
\input{dmarc}
\input{dmorg}
\input{dmwbs}
\input{dmproducts}
\input{dmroles}
\input{dmgroups}
\input{leadtutes}
\input{devprocess}
\input{probman}

\appendix
\newpage
\section{DM Product List \label{sect:prodlist}}

Refer to \citeds{LDM-148} for a detailed description of the meaning of each product referred to below.

\input{productlist}
\newpage
\input{wbslist}
\newpage
\input{DDMP}
\newpage
\input{trace}
%\input{precon}
\newpage
\input{refs}
\end{document}
