\paragraph*{1.02C.10.02.03: Developer Infrastructure, Software Distribution, Documentation Tooling, Communication Tooling}

This WBS element consists of services that support a large distributed
software team and its product. It includes systems that support current
best practices in software engineering such as continuous integration,
release management, software packaging and distribution, documentation
standards, and infrastructure and communication tooling supporting
development and team culture. All these services are oriented towards
developers, and some are also oriented towards users of the DM software
outside DM. While these are EVM deliverables, work is planned in such a
way to reserve effort for ad-hoc developer-driven requests, since these
are customer-oriented services that benefit from continuous improvement.

\begin{description}

\item[1.02C.10.02.03.01: Software Development Services]
  Continuous Integration service(s), repository management, code linters,
  software development environments.

\item[1.02C.10.02.03.02: Release Engineering]
  Work with the Release Manager
  (\hyperref[wbs:1.02C.02.02.02]{1.02C.02.02.02}) to provide portability
  testing, binary and containerized distribution, build tooling.

\item[1.02C.10.02.03.03: Documentation Tooling]
  Documentation standards, documentation linters, software and technical
  documentation production and publication, developer guide, user guide,
  tutorials, document discovery services.

\item[1.02C.10.02.03.04: Communication Tooling]
  Community forum, ChatOps.

\item[1.02C.10.02.03.05: Bug/Tracking Helpdesk]
  Bug Tracking, Helpdesk, Community Management

\end{description}
