\subsubsection*{1.02C.10.02: Quality Control, Dataspace Services, and Developer Infrastructure}

This WBS element consists of software, services, unit tests, integration tests, configuration and deployment automation, availability monitoring and documentation for: quality analysis, enabling of science analysis, automated quality control, verification and developer services.

\paragraph*{1.02C.10.02.01: Automated Software and Science Quality Control Service}
\label{wbs:1.02C.10.02.01}

This WBS element consists of software and services that support the
implementation of Data Management's plan to ensure the quality of the DM
Pipelines.

\begin{description}

\item[1.02C.10.02.01.01: SQuaSH]
  \label{wbs:1.02C.10.02.01.01}
  A harness for executing prepared tests automatically and continuously to
  characterise the algorithmic performance of the code, key aspects of the
  performance of the facility that are apparent in the data, its verification
  status, and uncover regressions to aid development.

\item[1.02C.10.02.01.02: Monitoring]
  A system for notifying when values for
  \hyperref[wbs:1.02C.10.02.01.01]{SQuaSH} metrics exceed notifiable limits.

\item[1.02C.10.02.01.03: Verification Reports Tooling]
  Using data produced by \hyperref[wbs:1.02C.10.02.01.01]{SQuaSH} to create
  verification reports and software release characterisations.

\item[1.02C.10.02.01.04: Alert QA harness]
  A harness to perform QA tests on the alert stream.

\end{description}

\paragraph*{1.02C.10.02.02: Science Platform Notebook Environment for QA, Commissioning \& User Science}

\begin{description}

\item[1.02C.10.02.02.01: Jupyter Notebook \& Templates]
  A set of notebooks, and templates for making them, that demonstrate key
  features of the capabilities of the system.

\item[1.02C.10.02.02.02: JupyterLab Deployment]
  Architecture, orchestration and deployment configuration for the Sciene
  Platform Notebook service for commissioning.

\item[1.02C.10.02.02.03: Custom Portals/Notebooks]
  \label{wbs:1.02C.10.02.02.03}
  This WBS element covers supporting the portals delivered by the SUIT team
  (\hyperref[wbs:1.02C.05.08]{1.02C.05.07}) post-delivery where they relate to
  QA and comissioning activities as necessary.

\item[1.02C.10.02.02.04: Notebook Software Environments]
  \label{wbs:1.02C.10.02.02.04}
  Production of environments (e.g. containers) suitable for the execution of
  \hyperref[wbs:1.02C.10.02.02.03]{custom portals/notebooks}.

\item[1.02C.10.02.02.05: Notebook Execution]
  The process to scale notebook execution so they can execute over a large
  dataset. This involves an interface to the batch workflow system.

\item[1.02C.10.02.02.06: Dataspace packaging]
  The packaging and configuration required to deploy the dataspace on a
  platform that is design-matched to the compute and filespace elements of the
  Archive Center dataspace (e.g. if the DAC compute is based on an OpenStack
  architecture, the deliverable of this WBS are the packages, configuration,
  automation deployment and instructions that would allow a Data Access Center
  at an international partner to deploy a Dataspace service on top of their
  open OpenStack compute for their own users).

\end{description}

\paragraph*{1.02C.10.02.03: Developer Infrastructure, Software Distribution, Documentation Tooling, Communication Tooling}

This WBS element consists of services that support a large distributed
software team and its product. It includes systems that support current
best practices in software engineering such as continuous integration,
release management, software packaging and distribution, documentation
standards, and infrastructure and communication tooling supporting
development and team culture. All these services are oriented towards
developers, and some are also oriented towards users of the DM software
outside DM. While these are EVM deliverables, work is planned in such a
way to reserve effort for ad-hoc developer-driven requests, since these
are customer-oriented services that benefit from continuous improvement.

\begin{itemize}

\item[1.02C.10.02.03.01: Software Development Services]
  Continuous Integration service(s), repository management, code linters,
  software development environments.

\item[1.02C.10.02.03.02: Release Engineering]
  Release management, portability testing, binary and containerized
  distribution, build tooling.

\item[1.02C.10.02.03.03: Documentation Tooling]
  Documentation standards, documentation linters, software and technical
  documentation production and publication, developer guide, user guide,
  tutorials, document discovery services.

\item[1.02C.10.02.03.04: Communication Tooling]
  Community forum, ChatOps.

\item[1.02C.10.02.03.05: Bug/Tracking Helpdesk]
  Bug Tracking, Helpdesk, Community Management

\end{itemize}
